\documentclass{article}
\begin{document}

\begin{enumerate}
\item Important
	\begin{enumerate}
		\item Is this a new position or someone has left? If so, why did he leave? Can I get his contacts?
		\item Is IT focused on Windows or Linux?
		\item Do you have company policies? Who writes them?
		\item Who will be my supervisor?
		\item Who will sit in same room with me?
	\end{enumerate}

\item Conditions
	\begin{enumerate}
		\item Where will I work? Can I see the room?
		\item Is smoking allowed inside the building? Is the rule strictly enforced?
		\item How strict are you about employers being late?
		\item When can I start working? When will salary start counting?
		\item Any health insurance plan?
		\item When can I have days off? How are they calculated?
		\item Can I leave for good reasons - lessons, medical, personal etc?
		\item Is there any place to eat?
		\item Is there any water machines?
	\end{enumerate}

\item Salary
	\begin{enumerate}
		\item Is salary decided by worked hours or by productivity? If by productivity, then how is success measured and who measures success?
		\item Is salary a fixed amount or is there some kind of bonus system?
		\item Under what conditions does salary increase?
		\item Will there be any new positions available in the near future? Any place for advancement?
	\end{enumerate}

\item Information Security-specific Questions
	\begin{enumerate}
		\item How can I be sure I won't be laid off/salary decreased soon after 27001 is implemented or the company is merged?
		\item What stage of 27001 implementation are you now? Can I see diagnostic results if there are any?
		\item Do you use COBIT os some other helper framework?
	\end{enumerate}
\end{enumerate}
\end{document}
